A finite-state morphological transducer for Kyrgyz

### 2012-03-13 paper/paper.tex
bib fixes
gone through TODO
beginning of section

%old lrec stuff doesn't work well =(
%\usepackage{lrec2006}

@@

\subsection{Morphological and orthographic words}

@@

While the phonological rules are not necessarily as closely tied to an accurate morphological analysis of what is going on as they could be, these few rules allowed fewer irregular continuation lexica to be created---most immediately by allowing the ablative and dative continuation lexica for 3rd person to behave similarly to that of 1st and 2nd person singular, and avoiding separate irregular continuation lexica for the other cases.  The direct result of this approach was a much smaller and simpler transducer.

@@

\bibliographystyle{lrec2006}
\bibliography{paper}

>>>>

%old lrec stuff doesn't work well =(
\usepackage{lrec2006}

@@

\subsection{Morphological and orthographic words}
Normal tokenisation often takes white space to be the delimiter between ``words''.  For analysis and generation, however, there are some morphophonological processes that work across the ``whitespace'' boundary.

@@

While the phonological rules are not necessarily as closely tied to an accurate morphological analysis of what is going on as they could be, these few rules allowed fewer irregular continuation lexica to be created---most immediately by allowing the ablative and dative continuation lexica for 3rd person to behave similarly to that of 1st and 2nd person singular, and avoiding separate irregular continuation lexica for the other cases.  The direct result of this approach was a much more concise description of the morphology in the lexicon file.

@@

\bibliographystyle{lrec2012}
\bibliography{paper}
